On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
chaz

Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning. More specifically, we show that matrices injective on a sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}). In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).

>>>>

Here, we prove very generally that uniqueness and stability is a typical property of sparse dictionary learning. More specifically, we show that matrices injective on a $k$-sparse domain are identifiable from \mbox{$N = m(k-1){m \choose k} + m$} noisy linear combinations of $k$ of their $m$ columns up to an error that is linear in the noise (Thm.~\ref{DeterministicUniquenessTheorem}). In fact, provided $n \geq \min(2k,m)$, in almost all cases the problem is well-posed, as per Hadamard \cite{Hadamard1902}, given a sufficient amount of data (Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}).
